Tools for reproducible ex-post survey data harmonization

### 2020-07-10 data-raw/article.Rmd
update article

---
title: "Tools for reproducible ex-post survey data harmonization"
subtitle: "The case of the Eurobarometer surveys"
author: "Daniel Antal, Marta Kolczynska"
date: "7/6/2020"
bibliography: [library.bib, packages.bib]
biblio-style: apalike
output:
  html_document: default
  word_document: default
---

>>>>

---
title: "Tools for reproducible ex-post survey data harmonization"
subtitle: "The case of the Eurobarometer surveys"
author: "Daniel Antal, Marta Kolczynska"
date: "7/10/2020"
bibliography: [library.bib, packages.bib]
biblio-style: apalike
output:
  html_document: default
  word_document: default
---
